Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-04 lloveras_2020.tex
retoques a captions, sugerencias Fede

\address[id=aff4]{Department of Climate and Space Sciences and Engineering (CLaSP), University of Michigan, 2455 Hayward Street, Ann Arbor, MI 48109-2143, USA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract 
\begin{abstract}
Observational tools play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to enhance their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of fundamental plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfvén Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

\subsection{DEMT reconstructions}\label{demt}

@@

\textcolor{red}{aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}

\subsection{AWSoM simulations}\label{awsom}

@@

\textcolor{red}{Podriamos comentar acá las mejoras hechas a la tomo desde la ultima publicacion.}
DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, \textcolor{red}{definir hollow-tom} and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.

@@

Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}. As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065 and 1.105\,\mrsun$. Black voxels correspond to non-reconstructed regions.

\textcolor{red}{
*Comentarios descriptivos sobre las rotaciones:
-Simetria
-CH
-Matcheo entre open-closed boundaries y las estructuras termodinamicas.
}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$ ,$1.065$ and $1.105\,\mrsun$, respectively. Black voxels correspond to non-reconstructed regions and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{rpoint_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Histogram of the temperature radial gradient along each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type 0 - down loops and type I - up loops), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels). for CR-2082. DEMT results of CR2082 are shown in blue while those of CR2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c, and \phi_h$ for CR2082 (top) and CR2208 (bottom). Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down! Aca hay que tomar una desicion para no marear al lector! Pero lo dejo asi internamente para compararlo con figura 5 y 6 del aper de Mac Cormack}}
\label{gradt_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_awsom_2082} but for AWSoM results.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_awsom_2208} but for AWSoM results.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged, in both rotations, of electron density (top) and electron temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ along all field lines of type I (in blue), of type II (in red) and of type III (in green) meeting the criteria listed in Section \ref{trace} for CR-2082 (top panel) and CR-2208 (bottom panel). In solid lines DEMT traced results and in dashed lines AWSoM results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions of (from left to right): the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all field lines traced in the streamer (type I, top panels), the boundary of the streamer (type II, mid panels) and the Coronal Holes (type III, bottom panels) for CR-2082. In blue the data of DEMT are shown while those of AWSoM in red. In each panel the median $m$ is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
\caption{Same as Figure \ref{histos_2082} but for CR2208.}
\label{histos_2208}
\end{center}
\end{figure}

>>>>

\address[id=aff4]{Department of Climate and Space Sciences and Engineering (CLaSP), University of Michigan, 2455 Hayward Street, Ann Arbor, MI 48109-2143, USA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Abstract 
\begin{abstract}
Observational tools play an essential role in advancing our understanding of the physics of the solar corona. They provide validation data to improve three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere, key to enhance their space weather forecasting capabilities. Solar rotational tomography (SRT) is currently the sole observational technique that provides an empirical 3D description of fundamental plasma parameters of the solar corona at a global scale. Based on EUV data of space borne instruments, SRT allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below 1.25 Rsun. We carry out a study of the corona combining tomographic reconstructions with MHD simulations of the latest version of the Alfv\'en Wave Solar Model (AWSoM) of the Space Weather Modeling Framework (SWMF). Target rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and the current declining phase of solar cycle 24. Tomographic reconstructions and results of the model are analyzed in distinct coronal magnetic structures. We study magnetically closed structures associated with the equatorial streamer belt, as well as magnetically open regions enclosing it. We report on the tomographic results in the different structures, their implications for the physics of the solar corona, and the capability of the AWSoM model to reproduce the tomographic reconstructions in different regions.

@@

\subsection{DEMT reconstructions}\label{demt} 
\textcolor{red}{*Tratado de imagenes}
\textcolor{red}{*FBE}
\textcolor{red}{*LDEM}

@@

\textcolor{red}{*aclarar que consideramos Ne como $\sqrt{<N_e ^2>}$.}

\textcolor{red}{*Mejoras de la tecnica con respecto a trabajos previos}

\subsection{AWSoM simulations}\label{awsom} 
\textcolor{red}{*Que es, que modela, que datos usa, y que se obtiene en general y en particular para este trabajo}

@@

DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, \textcolor{red}{definir hollow-tom} and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.

@@

Once the LDEM was determined for each rotation, the electron density $N_e$ and electron mean temperature $T_\textrm{m}$ were computed at each voxel of the tomographic computational grid by means of Equations \ref{momento1} and \ref{momento2}. As an example, Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show the results for both rotations at $r=1.025, 1.065$ and $1.105\,\mrsun$. Black voxels correspond to non-reconstructed regions.

\textcolor{red}{
*explicar voxel negros
*Comentarios descriptivos sobre las rotaciones:
-Simetria
-CH
-Matcheo entre open-closed boundaries y las estructuras termodinamicas.
}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2082_DEMT-EUVI_behind_H1-L3523_r3d_1105_Rsun.pdf}
\caption{Carrington maps of DEMT results: $N_e$ (left panels) and $T_\textrm{m}$ (right panels) for CR-2082. Top, middle and bottom panels show the results at three heliocentric heights, $1.025$, $1.065$ and $1.105\,\mrsun$ respectively. Black voxels correspond to non-reconstructed regions (see text in Section \ref{demt_res}) and thick-black curves indicate the open/closed boundaries.}
\label{carmaps_demt_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_full_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of each leg of type 0 (in cyan), type I (in blue), type II (in red) and type III (in green) at $1.105\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel). See Section \ref{trace} for a definition of the different types of legs.}
\label{rpoint_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for the different types of legs shown in Figure \ref{rpoint_demt} (same colour code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_down_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_2208_fulldemt_CH_up_Tm.eps}
\caption{Comparative statistical distributions of DEMT reults. From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average electron mean temperature $\aTm$, along all types of legs defined in Section \ref{trace}. Results of CR2082 are shown in blue while those of CR-2208 in red. In each panel the median $m$ is indicated.}
\label{histos_fulldemt}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ for CR-2082 (top) and CR-2208 (bottom). Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down! Aca hay que tomar una desicion para no marear al lector! Pero lo dejo asi internamente para compararlo con figura 5 y 6 del paper de Mac Cormack. Fede sugiere 6 graf, uno para cada tipo de linea (0, 1, 2).}}
\label{gradt_demt}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2082_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2082_185_short_1105_Rsun.pdf}
\caption{Carrington maps of density (left panels) and temperature (right panels)) obtained with AWSoM model for the three heights shown in Figure \ref{carmaps_awsom_2082}.}
\label{carmaps_awsom_2082}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_awsom_2208_185_short_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Te_awsom_2208_185_short_1105_Rsun.pdf}
\caption{Same as Figure \ref{carmaps_awsom_2208} for CR-2208.}
\label{carmaps_awsom_2208}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt}, using the density and temperature of AWSoM model to classify legs in type 1, 2 and 3.}
\label{rpoint_awsom}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Te_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged electron density (top) and temperature (bottom) for DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. The left (right) panels correspond to CR-2082 (CR2208). The vertical black line indicates the longitude-averaged latitudes of the open/close magnetic boundary.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2082_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_ne_cr2208_up_short.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/perfil_paper_te_cr2208_up_short.eps}
\caption{Average fits of $N_e(r)$ and $T_e(r)$ for all legs of type I (blue), type II (red) and type III (green) for CR-2082 (top panel) and CR-2208 (bottom panel) using DEMT (solid) and AWSoM (dashed) results.}
\label{perfiles_promedio}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_streamer_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_bound_up_Tm.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2082_demt_awsom_CH_up_Tm.eps}
\caption{Comparative statistical distributions for CR-2082 between DEMT (blue) and AWSoM (red). From left to right: the coronal base electron density $N_e(r=1.055\,\mrsun)$, the electron density scale height $\lN$ and the average $\aTm$ along the four types of legs considered in Section \ref{trace}. In each panel the median ($m$) is indicated.}
\label{histos_2082}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_streamer_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_bound_up_Tm.eps}\\
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_ne_1055.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_lambda_n.eps}
\includegraphics[width=0.31\textwidth,clip=]{figs/histo_2208_demt_awsom_CH_up_Tm.eps}
\caption{Same as Figure \ref{histos_2082} for CR-2208.}
\label{histos_2208}
\end{center}
\end{figure}
